---
title: "racewalk_dataprep"
format: html
---
# Load in libraries

```{r}
library(tidyverse)
library(readr)
```

# Read in data

Data was copied and pasted from [this link](https://www.watchathletics.com/page/5352/results-world-athletics-race-walking-team-championships-2024#google_vignette){target="_blank"} and then modified in an excel document to include  distance and sex.

That excel document is read in below.

```{r}
worldchamps <- read_csv("worldchamps.csv")
```

# Data Prep

Create a data set with only the 10k racers and separate the `TIME` variable so there is a `TIME` column and a `RECORD` column. Then split the `TIME` column into minutes and seconds and use them to calculate the `TIME` variable in total minutes. 

```{r}
ten <- worldchamps |> filter(DISTANCE == 10000) |> separate(TIME, into = c("TIME", "RECORD"), sep = " ") |> separate(TIME, into = c("MIN", "SEC"), sep = ":") |> mutate(MIN = as.double(MIN), SEC = as.double(SEC)) |> mutate(SEC = SEC/60) |> mutate(TIME = SEC + MIN) |> mutate(RECORD = replace_na(RECORD, replace = "NONE")) 
```

Create a data set with only the 20k racers and separate the `TIME` variable so there is a `TIME` column and a `RECORD` column. Then split the `TIME` column into hours, minutes, and seconds and use them to calculate the `TIME` variable in total minutes. 

```{r}
twenty <- worldchamps |> filter(DISTANCE == 20000) |> separate(TIME, into = c("TIME", "RECORD"), sep = " ") |> separate(TIME, into = c("HRS", "MIN", "SEC"), sep = ":") |> mutate(HRS = as.double(HRS), MIN = as.double(MIN), SEC = as.double(SEC)) |> mutate(HRS = HRS*60, SEC = SEC/60) |> mutate(TIME = HRS + SEC + MIN) |> mutate(RECORD = replace_na(RECORD, replace = "NONE")) 
```

Join the two datasets.

```{r}
complete <- full_join(ten, twenty)
```

Select the variables needed. 

```{r}
racewalking <- complete |> select(POS, COUNTRY, ATHLETE, RECORD, DISTANCE, GENDER, TIME)
```

Calculate a `SPEED` variable using `TIME` and `DISTANCE`. 

```{r}
racewalking_df <- racewalking |> mutate(SPEED= DISTANCE/TIME) 
```

Alter the values of the `GENDER` variable so that instead of (0,1) they are woman and man where *woman = 1* and *man = 0*.  

```{r}
gender <- racewalking_df |> mutate(GENDER = if_else(GENDER == 1, true = "Woman", false = "Man")) 
```

Make the `DISTANCE` variable a factor, not a double variable.

```{r}
distance <- gender |> mutate(DISTANCE = as.factor(DISTANCE))
```

Create a binary (0,1) variable for if a racer got a record, make sure to make the variable is a factor. 

```{r}
record <- distance |> mutate(REC = if_else(RECORD != "NONE", true = TRUE, false = FALSE))
```

Create another binary (0,1) variable for if a racer had a podium finish, make sure to make the variable is a factor as well. 

```{r}
podium <- record |> mutate(PODIUM = if_else(POS <= 3, true = TRUE, false = FALSE)) 
```

Write the csv file.

```{r}
write_csv(podium, "racewalking.csv")
```






